---
title: "Homework 1"
author: "Ke Ding"
date: "9/12/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem1:
part a)
The Euclidean distance are summerized below: 
ob1: 3.000000
ob2: 2.000000
ob3: 3.162278
ob4: 2.236068
ob5: 1.414214
ob6: 1.732051

part b)
Perform the knn when k=1, it is green since ob5 is closest to test data, and it is green.

part c)
Perform the knn when k=3, it is red, since it calculated the nearest 3 neighbors, which are red, green, and red for ob2, 5, and 6 respectively.

part d)
If the system is highly non-linear, that means it is very curvy and we need a flexible curve to capture those small variances, then small k is feasible for us. choose k from 1 to 10. 



```{r hw1}
library(class)
ob1<-cbind(0,3,0, "Red")
ob2<-cbind(2,0,0, "Red")
ob3<-cbind(0,1,3, "Red")
ob4<-cbind(0,1,2, "Green")
ob5<-cbind(-1,0,1, "Green")
ob6<-cbind(1,1,1, "Red")
data1<-rbind(ob1,ob2,ob3,ob4,ob5,ob6)
te_p<-cbind(0,0,0)
eucl_dis<-rdist(data1[,1:3],te_p)
train1<-data1[,1:3]
class<-data1[,4]
knn1<-knn(train1,te_p,class, k=1)
knn2<-knn(train1,te_p,class, k=3)
# eucl_dis_1<-as.numeric(dist(rbind(data[1,1:3],te_p)))
# eucl_dis_2<-as.numeric(dist(rbind(data[1,1:3],te_p)))
# eucl_dis_3<-as.numeric(dist(rbind(data[1,1:3],te_p)))
# eucl_dis_4<-as.numeric(dist(rbind(data[1,1:3],te_p)))
# eucl_dis_5<-as.numeric(dist(rbind(data[1,1:3],te_p)))
# eucl_dis_6<-as.numeric(dist(rbind(data[1,1:3],te_p)))

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
